### 2009-11-10 doc/tech_doc/infosys/infosys_technical.tex
Removing custom logger from ISIS documentation and fixing the line wraping at the scema file.

\textit{This section extensively uses terms defined in "Security Framework of ARC1" document"~\cite{arcsec}.}

@@

\textit{For information about sophisticated authorization policies and how to deploy various Policy Decision Point entities please see "Security Framework of ARC1" document"~\cite{arcsec}.}

@@

<!-- This is an initial and incomplete DRAFT which mainly concentrates on the structure but not on the actual names. Final version will use G
LUE-2.0 ternminology. -->

@@

  <xsd:complexType name="Logger_Type">
    <xsd:simpleContent>
      <xsd:extension base="xsd:string">
        <xsd:attribute name="level" default="INFO">
          <xsd:simpleType>
            <xsd:restriction base="xsd:string">
              <xsd:enumeration value="VERBOSE"/>
              <xsd:enumeration value="DEBUG"/>
              <xsd:enumeration value="INFO"/>
              <xsd:enumeration value="WARNING"/>
              <xsd:enumeration value="ERROR"/>
              <xsd:enumeration value="FATAL"/>
            </xsd:restriction>
          </xsd:simpleType>
        </xsd:attribute>
      </xsd:extension>
    </xsd:simpleContent>
  </xsd:complexType>

  <xsd:element name="Logger" type="icfg:Logger_Type">
      <xsd:annotation>
          <xsd:documentation xml:lang="en">
              File location where the log message is locally stored.
          </xsd:documentation>
      </xsd:annotation>
  </xsd:element>

@@

            <xsd:element name="Retry" type="xsd:string" minOccurs="0" maxOccurs="1" default="5">
                <xsd:annotation>
                    <xsd:documentation xml:lang="en">
                     Retry count. Specified how many times have an ISIS to timeout to handle it as.
                     unavailable. If there is no value specified the default value: 5 will be used..
                    </xsd:documentation>
                </xsd:annotation>
            </xsd:element>
        </xsd:sequence>
    </xsd:complexType>

@@

    <Service name="isis" id="isis1">
        <isis:DBPath>
            <!-- File location where the database is locally stored -->
        </isis:DBPath>
        <isis:endpoint>
            <!-- The URL where the service can be accessed from outside -->
        </isis:endpoint>
        <isis:InfoProviderISIS>
            <isis:URL>
                <!-- The URL of one or more ISIS where the other ISIS's can be queried. -->
            </isis:URL>
        </isis:InfoProviderISIS>
        <infosys:InfoRegister>
            <infosys:Period>
                <!-- How often should the service be registered. 
                For example: PT75S for 75 seconds -->
            </infosys:Period>
            <infosys:Endpoint>
                <!-- The URL where the service can be accessed from outside -->
            <infosys:Endpoint>
            <infosys:Expiration>
                <!-- The lifetime of the RegEntry provided by the service about itself.
                For example: PT5H for 5 hours -->
            </infosys:Expiration>
            <!-- The period of the repeating 
             registration will be the value given here in every ISIS cloud. -->
            <infosys:Registrar>
                <!-- Contact and behavior details of the Registrar element-->
                <infosys:URL><!-- Available endpoint URL of an ISIS representing the cloud --></infosys:URL>
                <infosys:Retry>4</infosys:Retry>        
            </infosys:Registrar>
        </infosys:InfoRegister>
    </Service>
  </Chain>
</ArcConfig>

>>>>

\textit{This section extensively uses terms defined in "Security Framework of WS-ARC" document"~\cite{arcsec}.}

@@

\textit{For information about sophisticated authorization policies and how to deploy various Policy Decision Point entities please see "Security Framework of WS-ARC" document"~\cite{arcsec}.}

@@

<!-- This is an initial and incomplete DRAFT which mainly concentrates on the structure
 but not on the actual names. Final version will use GLUE-2.0 ternminology. -->

@@

@@

            <xsd:element name="Retry" type="xsd:string" minOccurs="0" maxOccurs="1" 
            default="5">
                <xsd:annotation>
                    <xsd:documentation xml:lang="en">
                     Retry count. Specified how many times have an ISIS to timeout to
                     handle it as unavailable. If there is no value specified the default
                     value: 5 will be used.
                    </xsd:documentation>
                </xsd:annotation>
            </xsd:element>
        </xsd:sequence>
    </xsd:complexType>

@@

    <Service name="isis" id="isis1">
        <isis:DBPath>
            <!-- File location where the database is locally stored -->
        </isis:DBPath>
        <isis:endpoint>
            <!-- The URL where the service can be accessed from outside -->
        </isis:endpoint>
        <isis:InfoProviderISIS>
            <isis:URL>
                <!-- The URL of one or more ISIS where the other ISIS's can be queried. -->
            </isis:URL>
        </isis:InfoProviderISIS>
        <infosys:InfoRegister>
            <infosys:Period>
                <!-- How often should the service be registered. 
                For example: PT75S for 75 seconds -->
            </infosys:Period>
            <infosys:Endpoint>
                <!-- The URL where the service can be accessed from outside -->
            <infosys:Endpoint>
            <infosys:Expiration>
                <!-- The lifetime of the RegEntry provided by the service about itself.
                For example: PT5H for 5 hours -->
            </infosys:Expiration>
            <!-- The period of the repeating 
             registration will be the value given here in every ISIS cloud. -->
            <infosys:Registrar>
                <!-- Contact and behavior details of the Registrar element-->
                <infosys:URL>
                    <!-- Available endpoint URL of an ISIS representing the cloud -->
                </infosys:URL>
                <infosys:Retry>4</infosys:Retry>        
            </infosys:Registrar>
        </infosys:InfoRegister>
    </Service>
  </Chain>
</ArcConfig>
